Energy and the CES production function

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better formatting for column titles.

# This function is used in many places below.
myXTable <- function(data, caption, label, digits=2){
  table <- xtable(data, caption=caption, label=label, digits=digits)
  print(table, 
        caption.placement="top", 
        size="\\tiny", 
        include.rownames=FALSE, 
        math.style.negative=TRUE, 
        booktabs=TRUE)
}
@

@@

Table~\ref{tab:CES_alpha} shows 
the factor shares~($\alpha_i$ values) for all CES modeling decisions.
%
<<CES_alpha, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
           select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3),
         caption="Factor shares~($\\alpha$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
show factor shares ($\alpha$ values) for CES models for
Portugal and the UK, respectively.
See Table~\ref{tab:CES_abg_equations} for details on the calculation
of factor shares from fitted values of $\delta_1$ and $\delta$.
%
<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
  # Change nest to a nicer-looking nest string
  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
  # Add a label column
  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
  # Add row numbers to the label column
  bar_chart_data$label <- paste(paste0(1:length(bar_chart_data$label), ". "), bar_chart_data$label)
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  bar_chart_data <- melt(bar_chart_data, 
                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
                         value.name = "value", 
                         variable.name = "variable")
  bar_chart_data$variable <- plyr::mapvalues(bar_chart_data$variable, 
                                       from=c("alpha_1", "alpha_2", "alpha_3"), 
                                       to=c("alpha_k", "alpha_l", "alpha_e"))

@@

**** Is there a graph we want to make here? ---MKH ****
%
<<CES_sigma, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES") %>% 
           select(Country, model, flavor, energy, nest, CSP, sigma_1, sigma),
         caption="Factor substitution~($\\sigma$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

@@

Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
on fitted parameters for the Cobb-Douglas model and the exponential-only model.
The Cobb-Douglas models show lower $sse$ than the exponential-only models.
The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
<<Effect_of_CSP_CD, results="asis">>=
myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
           select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse),
         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
<<CD_coeffs, results="asis">>=
myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
           select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
         caption="Model parameters for all Cobb-Douglas models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

>>>>

# This function is used in many places below.
myXTable <- function(data, caption, label, digits=2){
  table <- xtable(data, caption=caption, label=label, digits=digits)
  print(table, 
        caption.placement="top", 
        size="\\tiny", 
        include.rownames=FALSE, 
        math.style.negative=TRUE, 
        sanitize.text.function=function(x){x},
        booktabs=TRUE)
}
@

@@

Table~\ref{tab:CES_alpha} shows 
the factor shares~($\alpha_i$ values) for all CES modeling decisions.
%
<<CES_alpha, results="asis">>=
data_CES_alpha <- filter(AllCoeffs, model=="CES" | model=="exp") %>% 
  select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
data_CES_alpha <- plyr::rename(data_CES_alpha, c("alpha_1" = "$\\alpha_1$",
                                                 "alpha_2" = "$\\alpha_2$",
                                                 "alpha_3" = "$\\alpha_3$"))
myXTable(data_CES_alpha,
         caption="Factor shares~($\\alpha$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
show factor shares ($\alpha$ values) for CES models for
Portugal and the UK, respectively.
See Table~\ref{tab:CES_abg_equations} for details on the calculation
of factor shares from fitted values of $\delta_1$ and $\delta$.
%
<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
  # Change nest to a nicer-looking nest string
  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
  # Add a label column
  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
  # Add row numbers to the label column
  bar_chart_data$label <- paste(paste0(1:length(bar_chart_data$label), ". "), bar_chart_data$label)
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  bar_chart_data <- melt(bar_chart_data, 
                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
                         value.name = "value", 
                         variable.name = "variable")
  bar_chart_data$variable <- plyr::mapvalues(bar_chart_data$variable, 
                                       from=c("alpha_1", "alpha_2", "alpha_3"), 
                                       to=c("alpha_k", "alpha_l", "alpha_e"))

@@

**** Is there a graph we want to make here? ---MKH ****
%
<<CES_sigma_table_data>>=
sigma_data <- filter(AllCoeffs, model=="CES") 
sigma_data <- plyr::rename(sigma_data, c("model" = "Model", "flavor" = "Type", "energy" = "Energy", "nest" = "Nest"))
@

<<CES_sigma, results="asis">>=
data_CES_sigma_raw <- sigma_data %>% select(Country, Model, Type, Energy, Nest, CSP, sigma_1, sigma)
data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
                                                         "sigma_1" = "$\\sigma_1$"))
myXTable(data_CES_sigma_raw,
         caption="Factor substitution~($\\sigma$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Factor substitution~($\\sigma$) for CES models. Inner nests.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Factor substitution~($\\sigma$) for CES models. Outer nests.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
on fitted parameters for the Cobb-Douglas model and the exponential-only model.
The Cobb-Douglas models show lower $sse$ than the exponential-only models.
The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
<<Effect_of_CSP_CD, results="asis">>=
data_CSP_CD <- filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
  select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse)
data_CSP_CD <- plyr::rename(data_CSP_CD, c("alpha_1" = "$\\alpha_1$", "alpha_2" = "$\\alpha_2$"))
myXTable(data_CSP_CD,
         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
<<CD_coeffs, results="asis">>=
data_CD_exp <- filter(AllCoeffs, model=="CD" | model=="exp") %>% 
  select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)
data_CD_exp <- plyr::rename(data_CD_exp, c("alpha_1" = "$\\alpha_1$", 
                                           "alpha_2" = "$\\alpha_2$", 
                                           "alpha_3" = "$\\alpha_3$"))
myXTable(data_CD_exp,
         caption="Model parameters for all Cobb-Douglas models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
